Conceptualizing open health data platforms for low- and middle income countries

### 2024-05-16 index.qmd
update Digital Public Goods table

| Category  | Component | Digital Public Good |
|:----------|:----------|:--------------------|
| **Interoperability layer (IOL)** | IOL | [OpenHIM](http://openhim.org) |
| **Registry Services** | Client Registry (CR) | [SanteMPI](https://help.santesuite.org/product-overview/santesuite-products/master-patient-index-santempi) |
| | | [JeMPI](https://jembi.gitbook.io/jempi/) |
| | | [OpenCR](https://www.openclientregistry.org/) |
| | Facility Registry (FR) | [Global Open Facility Registry (GOFR)](https://github.com/intrahealth/gofr) |
| | Health Worker Registry (HWR) | [iHRIS](https://www.ihris.org/ihris-50) |
| | Terminology Service (TS) | [OCL Terminology Service](https://openconceptlab.org/terminology-service/) |
| | Product Catalog (PC) | not available |
| **Business Domain Services** | Shared Health Record (SHR) | [HAPI FHIR](https://hapifhir.io/) |
| | | [Fhirbase](https://www.health-samurai.io/fhirbase) |
| | | [FHIR Server for Azure](https://github.com/microsoft/fhir-server) |
| | | [I-TECH-UW SHR](https://github.com/I-TECH-UW/shared-health-record) |
| | Health Management Information System (HMIS) | [DHIS2](http://dhis2.org/) |
| | Finance and Insurance Service (FIS) | [OpenIMIS](http://openimis.org/) |
| | Logistics Management Information System (LMIS) | [OpenLMIS](http://openlmis.org/) |
| **Generic** | Identity and Access Management (IAM) | [Keycloak](https://www.keycloak.org/) |
| | Gateway & proxy | [FHIR Information Gateway](https://github.com/google/fhir-gateway) |
| | Admin dashboard for SHR | [OpenSRP FHIR Web](https://github.com/onaio/fhir-web) |
| | Configuration and deployment | [Instant OpenHIE](https://jembi.gitbook.io/instant-v2/) |

: Overview of current open source implementations of components included in the OpenHIE specification that are FHIR-compatible. The category Analytics Services is not a part of the original OpenHIE and is discussed in the paper. Point-of-Service systems are excluded for brevity. A systematic review of such digital public goods is beyond the scope of this document. {#tbl-digital-public-goods .striped .hover .responsive}

>>>>

| Category  | Component | Digital Public Good |
|:----------|:----------|:--------------------|
| **Interoperability layer (IOL)** | IOL | [OpenHIM](http://openhim.org) |
| | | [mHero](https://www.mhero.org/technology) |
| | | [OpenFN](https://docs.openfn.org/) |
| **Registry Services** | Client Registry (CR) | [SanteMPI](https://help.santesuite.org/product-overview/santesuite-products/master-patient-index-santempi) |
| | | [JeMPI](https://jembi.gitbook.io/jempi/) |
| | | [OpenCR](https://www.openclientregistry.org/) |
| | | [OpenCRVS](https://www.opencrvs.org/) |
| | Facility Registry (FR) | [Global Open Facility Registry (GOFR)](https://github.com/intrahealth/gofr) |
| | | [GeoPrism Registry (GPR)](https://geoprismregistry.com/) `|
| | Health Worker Registry (HWR) | [iHRIS](https://www.ihris.org/ihris-50) |
| | Terminology Service (TS) | [OCL Terminology Service](https://openconceptlab.org/terminology-service/) |
| | Product Catalog (PC) | [PCMT](https://productcatalog.io/) |
| **Business Domain Services** | Shared Health Record (SHR) | [HAPI FHIR](https://hapifhir.io/) |
| | | [Fhirbase](https://www.health-samurai.io/fhirbase) |
| | | [FHIR Server for Azure](https://github.com/microsoft/fhir-server) |
| | | [I-TECH-UW SHR](https://github.com/I-TECH-UW/shared-health-record) |
| | Health Management Information System (HMIS) | [DHIS2](http://dhis2.org/) |
| | Finance and Insurance Service (FIS) | [OpenIMIS](http://openimis.org/) |
| | Logistics Management Information System (LMIS) | [OpenLMIS](http://openlmis.org/) |
| | | [OpenBoxes](https://openboxes.com/features/) |
| **Generic** | Identity and Access Management (IAM) | [Keycloak](https://www.keycloak.org/) |
| | Gateway & proxy | [FHIR Information Gateway](https://github.com/google/fhir-gateway) |
| | Admin dashboard for SHR | [OpenSRP FHIR Web](https://github.com/onaio/fhir-web) |
| | Configuration and deployment | [Instant OpenHIE](https://jembi.gitbook.io/instant-v2/) |

: Overview of current open source implementations of components that fit in the OpenHIE specification. The category Analytics Services is not a part of the original OpenHIE and is discussed in the paper. Point-of-Service systems are excluded for brevity.List compiled using [Global Goods for Digital Health](https://digitalsquare.org/digital-health-global-goods), [Digital Public Goods Alliance](https://digitalpublicgoods.net/) and search of open source code repositories.  A systematic review of such digital public goods is beyond the scope of this document.  {#tbl-digital-public-goods .striped .hover .responsive}

### 2024-05-16 index.tex
update Digital Public Goods table

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2558}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2558}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4884}}@{}}
\caption{Overview of current open source implementations of components
included in the OpenHIE specification that are FHIR-compatible. The
category Analytics Services is not a part of the original OpenHIE and is
discussed in the paper. Point-of-Service systems are excluded for
brevity. A systematic review of such digital public goods is beyond the
scope of this document.}\label{tbl-digital-public-goods}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Category
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Component
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Digital Public Good
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Category
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Component
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Digital Public Good
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\textbf{Interoperability layer (IOL)} & IOL &
\href{http://openhim.org}{OpenHIM} \\
\textbf{Registry Services} & Client Registry (CR) &
\href{https://help.santesuite.org/product-overview/santesuite-products/master-patient-index-santempi}{SanteMPI} \\
& & \href{https://jembi.gitbook.io/jempi/}{JeMPI} \\
& & \href{https://www.openclientregistry.org/}{OpenCR} \\
& Facility Registry (FR) &
\href{https://github.com/intrahealth/gofr}{Global Open Facility Registry
(GOFR)} \\
& Health Worker Registry (HWR) &
\href{https://www.ihris.org/ihris-50}{iHRIS} \\
& Terminology Service (TS) &
\href{https://openconceptlab.org/terminology-service/}{OCL Terminology
Service} \\
& Product Catalog (PC) & not available \\
\textbf{Business Domain Services} & Shared Health Record (SHR) &
\href{https://hapifhir.io/}{HAPI FHIR} \\
& & \href{https://www.health-samurai.io/fhirbase}{Fhirbase} \\
& & \href{https://github.com/microsoft/fhir-server}{FHIR Server for
Azure} \\
& & \href{https://github.com/I-TECH-UW/shared-health-record}{I-TECH-UW
SHR} \\
& Health Management Information System (HMIS) &
\href{http://dhis2.org/}{DHIS2} \\
& Finance and Insurance Service (FIS) &
\href{http://openimis.org/}{OpenIMIS} \\
& Logistics Management Information System (LMIS) &
\href{http://openlmis.org/}{OpenLMIS} \\
\textbf{Generic} & Identity and Access Management (IAM) &
\href{https://www.keycloak.org/}{Keycloak} \\
& Gateway \& proxy & \href{https://github.com/google/fhir-gateway}{FHIR
Information Gateway} \\
& Admin dashboard for SHR &
\href{https://github.com/onaio/fhir-web}{OpenSRP FHIR Web} \\
& Configuration and deployment &
\href{https://jembi.gitbook.io/instant-v2/}{Instant OpenHIE} \\
\end{longtable}

>>>>

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2558}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2558}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4884}}@{}}
\caption{Overview of current open source implementations of components
that fit in the OpenHIE specification. The category Analytics Services
is not a part of the original OpenHIE and is discussed in the paper.
Point-of-Service systems are excluded for brevity.List compiled using
\href{https://digitalsquare.org/digital-health-global-goods}{Global
Goods for Digital Health},
\href{https://digitalpublicgoods.net/}{Digital Public Goods Alliance}
and search of open source code repositories. A systematic review of such
digital public goods is beyond the scope of this
document.}\label{tbl-digital-public-goods}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Category
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Component
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Digital Public Good
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Category
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Component
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Digital Public Good
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\textbf{Interoperability layer (IOL)} & IOL &
\href{http://openhim.org}{OpenHIM} \\
& & \href{https://www.mhero.org/technology}{mHero} \\
& & \href{https://docs.openfn.org/}{OpenFN} \\
\textbf{Registry Services} & Client Registry (CR) &
\href{https://help.santesuite.org/product-overview/santesuite-products/master-patient-index-santempi}{SanteMPI} \\
& & \href{https://jembi.gitbook.io/jempi/}{JeMPI} \\
& & \href{https://www.openclientregistry.org/}{OpenCR} \\
& & \href{https://www.opencrvs.org/}{OpenCRVS} \\
& Facility Registry (FR) &
\href{https://github.com/intrahealth/gofr}{Global Open Facility Registry
(GOFR)} \\
& & \href{https://geoprismregistry.com/}{GeoPrism Registry (GPR)} ` \\
& Health Worker Registry (HWR) &
\href{https://www.ihris.org/ihris-50}{iHRIS} \\
& Terminology Service (TS) &
\href{https://openconceptlab.org/terminology-service/}{OCL Terminology
Service} \\
& Product Catalog (PC) & \href{https://productcatalog.io/}{PCMT} \\
\textbf{Business Domain Services} & Shared Health Record (SHR) &
\href{https://hapifhir.io/}{HAPI FHIR} \\
& & \href{https://www.health-samurai.io/fhirbase}{Fhirbase} \\
& & \href{https://github.com/microsoft/fhir-server}{FHIR Server for
Azure} \\
& & \href{https://github.com/I-TECH-UW/shared-health-record}{I-TECH-UW
SHR} \\
& Health Management Information System (HMIS) &
\href{http://dhis2.org/}{DHIS2} \\
& Finance and Insurance Service (FIS) &
\href{http://openimis.org/}{OpenIMIS} \\
& Logistics Management Information System (LMIS) &
\href{http://openlmis.org/}{OpenLMIS} \\
& & \href{https://openboxes.com/features/}{OpenBoxes} \\
\textbf{Generic} & Identity and Access Management (IAM) &
\href{https://www.keycloak.org/}{Keycloak} \\
& Gateway \& proxy & \href{https://github.com/google/fhir-gateway}{FHIR
Information Gateway} \\
& Admin dashboard for SHR &
\href{https://github.com/onaio/fhir-web}{OpenSRP FHIR Web} \\
& Configuration and deployment &
\href{https://jembi.gitbook.io/instant-v2/}{Instant OpenHIE} \\
\end{longtable}
